The Astropy Project

### 2017-11-27 main.tex
Correct grammar and unify verbiage
Consistently and correctly use plural 'Quantity objects' everywhere (instead of 'the quantity object')

The \texttt{astropy.units} subpackage adds support for representing units and
numbers with associated units --- ``quantities'' --- in code.
Historically, quantities in code have often been represented simply as numbers,
with units implied or noted via comments in the code because of considerations
about speed: having units associated with numbers inherently adds overhead to
numerical operations.
In \texttt{astropy.units}, \texttt{Quantity} objects extend \texttt{numpy}
array object and have been designed with speed in mind.

@@

The \texttt{Quantity} object extends
the \texttt{numpy.ndarray} object and therefore
works well with many of the functions in \texttt{numpy} that support
array operations. For example, \texttt{Quantity} objects with angular
units can be directly passed in to the trigonometric functions implemented in
\texttt{numpy}. The units are internally converted to radians (what the \texttt{numpy}
trigonometric functions expect) before being passed to \texttt{numpy}.

>>>>

The \texttt{astropy.units} subpackage adds support for representing units and
numbers with associated units --- ``quantities'' --- in code.
Historically, quantities in code have often been represented simply as numbers,
with units implied or noted via comments in the code because of considerations
about speed: having units associated with numbers inherently adds overhead to
numerical operations.
In \texttt{astropy.units}, \texttt{Quantity} objects extend \texttt{numpy}
array objects and have been designed with speed in mind.

@@

\texttt{Quantity} objects extend
\texttt{numpy.ndarray} objects and therefore
work well with many of the functions in \texttt{numpy} that support
array operations. For example, \texttt{Quantity} objects with angular
units can be directly passed in to the trigonometric functions implemented in
\texttt{numpy}. The units are internally converted to radians (what the \texttt{numpy}
trigonometric functions expect) before being passed to \texttt{numpy}.
